---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kaefa

The goal of kaefa is to improving research capability to identify unexplained factor structure with complexly cross-classified multilevel structured data in R environment with automatory exploratory factor analysis (aefa) framework

## Installation

You can install kaefa from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("seonghobae/kaefa")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
library('kaefa')
mod1 <- estIRT(mirt::Science)
```

## software quality information
### ubuntu and mac environment
[![Travis-CI Build Status](https://travis-ci.org/seonghobae/kaefa.svg?branch=master)](https://travis-ci.org/seonghobae/kaefa)
### windows environment
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/seonghobae/kaefa?branch=master&svg=true)](https://ci.appveyor.com/project/seonghobae/kaefa)
### code quality
[![Coverage Status](https://img.shields.io/codecov/c/github/seonghobae/kaefa/master.svg)](https://codecov.io/github/seonghobae/kaefa?branch=master)

[Contributor Code of Conduct](CONDUCT.md)
